---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
  [![R-CMD-check](https://github.com/amcdavid/Genesee/workflows/R-CMD-check/badge.svg)](https://github.com/amcdavid/Genesee/actions)
  <!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Genesee

<!-- badges: start -->
<!-- badges: end -->

The goal of Genesee is to set up assay-specific analysis templates for various transcriptomic modalities, including scRNAseq, scVDJ and bulk RNAseq. 

## Installation

You can install it from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("amcdavid/Genesee")
```

You will also need to install GeneseeSC and GeneseeBulk, which contain the templates for this to be useful.

## Example

Initialize a project titled 'title' at 'path/to/projects/investigator/title' and copy down scRNA template files.

```{r example, eval = FALSE}
library(Genesee)
library(GeneseeSC)
genesee_skeleton('path/to/projects', 'investigator', 'title', author = 'Andrew', project_type = 'scRNA')
```

